Building a framework to perform automated verification of solar photovoltaic off-grid systems

### 2018-10-10 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated journal files

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{A}{ccording} to \cite{Coelho} there are presently 1.3 billion people with no access to electricity worldwide. 
%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.

Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). Only a niche market a few years ago, PV are now becoming a mainstream electricity provider, changing the way the world is powered. Based in data from \cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV. 
%The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
The renewable energy leads to an advance all over the world by protecting the environment: it is clean,
%(low greenhouse gases emissions)
operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}. Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
% 
%The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy.

Apart from PV modules; the PV systems consist of battery bank, controller, and inverter, plus the load. Moreover, the optimum sizing of these devices is important for reliable operation. Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}. Furthermore, there is the need for proper modeling and simulation tools for people involved in their application. In order to validate or even simulate a potential PV solution, there are a myriad of tools.

@@

Desiging any complex system, as a PV for example, more time is spent on verification than on construction, as shown in \cite{Baier}. Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Programs may be viewed as mathematical objects with behavior that is, in principle, well determined. This makes it possible to specify programs using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the program meets its specification, as defined by \cite{Trindade}.

This area of research is referred as formal methods as defined in \cite{Clarkeetal}.
% Their aim is to establish system correctness with mathematical rigor. 
In the recent decades, research in formal methods has led to the development of very promising verification techniques that facilitate the early detection of bugs in order to ensure the correctness of the system.

@@

%Bringing this technique to solar PV systems, i
Instead of finding a bug or a software inconsistence, the present work aim to verify a PV system, informing in which condition the project do not meet user requirements or will fail, as shown in Fig.\ref{fig:flowchartgeneral}. 
%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}. 
That is the main contribution of this paper.

@@

The remainder of this paper is organized as follows: Sect. 2 gives a background of solar PV systems. Section 3 describes the design and validation of a solar PV system. Section 4 describes the formal mathematical modeling of a generic PV system. Section 5 presents the automated verification theory, including details of the ESBMC process. The methodology is presented at Section 6. Section 7 discusses the related work. Section 8 presents the conclusion and describes future work. At the end of the paper, there is a list of all nomenclatures used at the text.

\section{Solar Photovoltaic System }
According to \cite{Roy}, a PV system is designed to give the electric supply to a load. This load can be either Alternate Current (AC) type or Direct Current (DC) type. Electric supply can be needed either in daytime or evening time (in particular cases, in both times). %The most basic PV system can give supply only in daytime.  
For night hours or rainy days, one needed to have batteries, where power can be stored and used \cite{Gules}.

PV systems are broadly classified into three distinct types, as described by \cite{Mohanty}: Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, Grid-connected systems, and solar PV hybrid system, where another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.

As the goal of this work is just the solutions aimed to isolated/ off-grid application, therefore it is not considered the on-grid or hybrid configurations.

%\begin{itemize}
%\item Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid. Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants; 
%\item Grid-connected systems, where the solar PV system is connected to the grid. The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards. Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode; 
%\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand. In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
%\end{itemize}

Specifically concerning isolated communities, 
% depending on the type of load, cost, resources availability, and requirements of the load, 
standalone systems can be split into several categories. However, the configuration that is most common nowadays is the regulated standalone system with battery and AC load. This configuration includes PV array, battery, MPPT and AC load. Battery is used to store the extra power of PV system. A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module. Extra charging and deep discharging can reduce the battery life \cite{Kim}. Because of the AC load, an inverter (DC to AC converter) is required. 
%This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.

The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. %That resource is found at modern PV systems and is strongly indicated due to its advantages.

@@

\section{Design and Validation of a Solar photovoltaic system}
The design and validation of a PV system can be done by hand or with the aid of a software tool.

In order to address different aspects of project system and systems design, there is a myriad of public domain and commercial software available for the PV market. According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization). 
%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
%
%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice. 
In this work, were evaluated the most popular tools, as PVWatts, SAM, Homer Pro, RETScreen Expert, and Hybrid2.

@@

Table \ref{table:softwares} summarizes the off-the-shelf tools mentioned in this paper.  Where just Hybrid2 do not have technical support; only HOMER Pro, and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; and that only HOMER Pro and RETScreen Expert are complete, including economical analysis or even optimization-sensitive analysis. However, only paid version of those softwares have all the features, and they run only at Windows-based operational systems. RETScreen and HOMER have a free web-based version but with limited resources.

@@

\subsection{PV generator (cell, module, array) }
A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
%In the present modeling, the focus is only on cell/module/array.

The basic element of a PV system is the PV cell, also called a solar cell. A PV / solar cell is a semiconductor device that can convert solar energy into DC electricity. 
%The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun). When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}. If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
To increase their utility, a number of individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or module).

%For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series. In addition, to achieve the desired voltage and current, modules are wired in series and parallel into what is called a PV Array, as shown in Fig.\ref{fig:celmodarray}. The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands. 
%
%\begin{figure}[h]
%\includegraphics[width=0.4\textwidth]{celmodarray}
%\centering
%\caption{PV cell, module and array (Source: \cite{SamlexSolar})}
%\label{fig:celmodarray}
%\end{figure}
%
The PV modules are generally rated under standard test conditions (STC), and the parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution. However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
%, which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5. The parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution. However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
%
%These uncertainties lead to either over- or underestimation of energy yield from PV modules. An overestimation up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}. The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}. 
%
%Modeling PV modules is one of the major components responsible for proper functioning of PV systems. However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage. Therefore, perfect modeling is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.
% 
%Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.

@@

The 1-diode model, shown by Fig. \ref{fig:equivckt}, whose equation to relate the output current, $I$, to the output voltage, $V$, is described in Equation \ref{eq:1diodemodel}.

\begin{equation}
\label{eq:1diodemodel}
I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right] 
\end{equation}

Where:
\begin{itemize}
\item $I_{ph}$ is the photocurrent delivered by the constant current source; 
\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed;
	\begin{itemize}
	\item $ N=1 $ in a single cell configuration. 	
	\end{itemize}	  
\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; 
	\begin{itemize}
	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
	\end{itemize}
\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
	\begin{itemize}
	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); 
	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
	\item $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
	\end{itemize}	 
\end{itemize}

@@

Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.

\begin{equation}
\label{eq:Isc}
I_{sc}=I_{ph}\vert_{V=0}
\end{equation}

@@

As shown by \cite{Saloux} the voltage and the current at the maximum power point and consequently the maximum output power, can be expressed by Equations \ref{eq:Vmfinal}, \ref{eq:Imfinal}, and \ref{eq:Pm}. These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.

\begin{equation}
\label{eq:Vmfinal}
V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) 
\end{equation}

@@

However, the photocurrent delivered by the constant current source ($ I_{ph} $) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers. Therefore, Equation \ref{eq:Iph} is used to calculate the photocurrent as function of irradiance and temperature \cite{Villalva}.

\begin{equation}
\label{eq:Iph}
I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right] 
\end{equation}

@@

In Equation \ref{eq:Iph}, $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) and corresponds to the photocurrent obtained from a given PV cell working at (STC or standard test conditions) reference conditions (provided by PV manufacturers). $ I_{ph,ref} $ can also be approximated to the reference short-circuit current that is provided by PV manufacturers ($ I_{sc,ref} $) as shown by \cite{Jakhrani}.

The cell temperature ($ T $) can be obtained from \cite{Ross} and is shown in Equation \ref{eq:Tcell}.

\begin{equation}
\label{eq:Tcell}
T = T_{air} + \dfrac{NOCT-20}{800}G
\end{equation}

@@

The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. Using the maximum power point current equation (Equation \ref{eq:Pm}) and the saturation current in the reference temperature given by Equation \ref{eq:I0}, the diode quality coefficient is determined by Equation \ref{eq:a}.

\begin{equation}
\label{eq:a}
a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) }
\end{equation}

@@

First is necessary to correct the energy consumption that was estimated to the load ($E_{consumption}$). That is done by Equation \ref{eq:Ecorrected}, according \cite{Pinho}. Where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.

\begin{equation}
\label{eq:Ecorrected}
E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }
\end{equation}

The total minimum number of solar panels necessary($ N_{TPmin} $) is calculated by Equation \ref{eq:NTPmin}, and the check is done with the Equation \ref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from Equation \ref{eq:NTPmin}.

\begin{equation}
\label{eq:NTPmin}
N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}
\end{equation}

@@

Particularly, the total number of panels is series ($ N_{PSmin} $) and parallel ($ N_{PPmin} $) are given by the Equations \ref{eq:NPSmin} and \ref{eq:NPPmin}, respectively. With the check did by Equations \ref{eq:NPS} and \ref{eq:NPP}. $ V_{system} $ is the DC voltage of the bus, and is a design decision (normally 12, 24 or 48 V).

\begin{equation}
\label{eq:NPSmin}
N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}
\end{equation}

@@

Several models have been presented in the literature, as shown by \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}. However, regardless of the model, normally the following parameters are required:

\begin{itemize}
\item Nominal capacity ($ q_{max} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery
%, under predetermined discharge conditions.
\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. 
%Obviously $ 0<SOC<1 $. 
If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). 
%It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
%\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
\end{itemize}

>>>>

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{A}{ccording} to \cite{Coelho} there are presently 1.3 billion people with no access to electricity worldwide. 
%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
%
%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
Only a niche market a few years ago, solar photovoltaic (PV) are now becoming a mainstream electricity provider.
% changing the way the world is powered. 
Based in data from \cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV. 
%The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
%The renewable energy leads to an advance all over the world by protecting the environment: it is clean,
%(low greenhouse gases emissions)
%operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}. 
%Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
% 
%The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy.

%Apart from PV modules; the 
%PV systems consist of PV modules, battery bank, controller, and inverter, plus the load. %Moreover, the optimum sizing of these devices is important for reliable operation.
%Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}. %Furthermore, there is the need for proper modeling and simulation tools for people involved in their application. 
In order to validate or even simulate a potential PV solution, there are a myriad of tools available at the market.

@@

Desiging any complex system, as a PV, more time is spent on verification than on construction, as shown in \cite{Baier}. Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Programs may be viewed as mathematical objects. 
%with behavior that is, in principle, well determined. 
 This makes it possible to specify systems as programs using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the program meets its specification.%, as defined by \cite{Trindade}.

This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
% Their aim is to establish system correctness with mathematical rigor. 
In the recent decades, research in formal methods has led to the development of very promising verification techniques.
% that facilitate the early detection of bugs in order to ensure the correctness of the system.

@@

%Bringing this technique to solar PV systems, i
%Instead of finding a bug or a software inconsistence, t
The present work aim to verify a PV system, informing in which condition the project do not meet user requirements or will fail, as shown in Fig.\ref{fig:flowchartgeneral}. 
%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}. 
That is the main contribution of this paper.

@@

The remainder of this paper is organized as follows: Section II gives the background. Section III describes the design and validation of PV system. Section IV describes the mathematical modeling. Section V presents the automated verification. The methodology is presented at section VI. Section VII is devoted to the results, and section VIII to the related work. Section IX presents the conclusion and describes future work.

\section{Solar Photovoltaic System }
According to \cite{Roy}, a PV system is designed to give the electric supply to a load. This load can be either Alternate Current (AC) type or Direct Current (DC) type. Electric supply can be needed either in daytime or evening time. 
%(in particular cases, in both times). %The most basic PV system can give supply only in daytime.  
For night hours or rainy days, one needed to have batteries, where power can be stored and used.% \cite{Gules}.

PV systems are broadly classified into three distinct types, as described by \cite{Mohanty}: (1) standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, (2) grid-connected systems, and (3) solar PV hybrid system, where another source(s) of energy can work together with the solar PV. % system to provide the required demand.
%, such as wind, biomass or diesel, 
%As the goal of this work is just the solutions aimed to isolated/ off-grid application, %therefore it is not considered the on-grid or hybrid configurations.
%
%\begin{itemize}
%\item Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid. Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants; 
%\item Grid-connected systems, where the solar PV system is connected to the grid. The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards. Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode; 
%\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand. In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
%\end{itemize}

Specifically concerning isolated communities, 
%standalone systems are one the most used solutions, and 
% depending on the type of load, cost, resources availability, and requirements of the load, 
%standalone systems 
%can be split into several categories. However, 
the configuration that is most common nowadays is the regulated standalone system with battery and AC load. This configuration includes PV array, batteries, charge controller, inverter, and AC load.
%PV array, battery, MPPT and AC load. Battery is used to store the extra power of PV system. A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module. Extra charging and deep discharging can reduce the battery life \cite{Kim}. Because of the AC load, an inverter (DC to AC converter) is required. 
%This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. %That resource is found at modern PV systems and is strongly indicated due to its advantages.

@@

\section{Design and Validation of a Solar photovoltaic system}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
%
In order to address different aspects of project system and systems design, there is a myriad of tools. 
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
The capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization). 
%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
%
%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice. 
In this work, were evaluated the most popular tools, as PVWatts, SAM, Homer Pro, RETScreen Expert, and Hybrid2.

@@

Table \ref{table:softwares} summarizes the off-the-shelf tools mentioned in this paper.  Where just Hybrid2 do not have technical support; only HOMER Pro, and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; and that only HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis. However, only paid version of those softwares have all the features, and they run only at Windows operational systems. RETScreen and HOMER have a free web-based version but with limited resources.

@@

\subsection{PV generator (cell, module, array) }
%A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
%In the present modeling, the focus is only on cell/module/array.
%
The basic element of a PV system is the PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
%The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun). When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}. If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
To increase their utility, a number of individual PV cells are interconnected together in a %sealed, weatherproof 
package called panel or module.

%For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series. In addition, to achieve the desired voltage and current, modules are wired in series and parallel into what is called a PV Array, as shown in Fig.\ref{fig:celmodarray}. The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands. 
%
%\begin{figure}[h]
%\includegraphics[width=0.4\textwidth]{celmodarray}
%\centering
%\caption{PV cell, module and array (Source: \cite{SamlexSolar})}
%\label{fig:celmodarray}
%\end{figure}
%
The PV modules are generally rated under standard test conditions (STC), and the parameters required for the input of the PV modules are relying on meteorological conditions.
%the meteorological conditions of the area to be serviced by PV solution. %However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
%, which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5. The parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution. However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
%
%These uncertainties lead to either over- or underestimation of energy yield from PV modules. An overestimation up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}. The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}. 
%
%Modeling PV modules is one of the major components responsible for proper functioning of PV systems. However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage. Therefore, perfect modeling is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.
% 
%Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.

@@

The 1-diode model, shown by Fig. \ref{fig:equivckt}, whose equation to relate the output current, $I$, to the output voltage, $V$, is described in Equation \ref{eq:1diodemodel}. 
\begin{equation}
\label{eq:1diodemodel}
I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right] 
\end{equation}

Where:
\begin{itemize}
\item $I_{ph}$ is the photocurrent delivered by the constant current source; 
\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed; $ N=1 $ in a single cell configuration.
%	\begin{itemize}
%	\item $ N=1 $ in a single cell configuration. 	
%	\end{itemize}	  
\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes.
%	\begin{itemize}
%	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
%	\end{itemize}
\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
	\begin{itemize}
	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); 
	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
	\item $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
	\end{itemize}	 
\end{itemize}

@@

Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.
\begin{equation}
\label{eq:Isc}
I_{sc}=I_{ph}\vert_{V=0}
\end{equation}

@@

As shown by \cite{Saloux} the voltage and the current at the maximum power point and consequently the maximum output power, can be expressed by Equations \ref{eq:Vmfinal}, \ref{eq:Imfinal}, and \ref{eq:Pm}. %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
\begin{equation}
\label{eq:Vmfinal}
V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) 
\end{equation}

@@

However, the photocurrent delivered by the constant current source ($ I_{ph} $) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers. Therefore, Equation \ref{eq:Iph} is used to calculate the photocurrent as function of irradiance and temperature \cite{Villalva}.
\begin{equation}
\label{eq:Iph}
I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right] 
\end{equation}

@@

In Equation \ref{eq:Iph}, $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) and corresponds to the photocurrent obtained from a given PV cell working at reference conditions (provided by PV manufacturers). $ I_{ph,ref} $ can also be approximated to the reference short-circuit current that is provided by PV manufacturers ($ I_{sc,ref} $) as shown by \cite{Jakhrani}.

The cell temperature ($ T $) can be obtained from \cite{Ross} and is shown in Equation \ref{eq:Tcell}.
\begin{equation}
\label{eq:Tcell}
T = T_{air} + \dfrac{NOCT-20}{800}G
\end{equation}

@@

%The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
Using the maximum power point current equation (Equation \ref{eq:Pm}) and the saturation current in the reference temperature given by Equation \ref{eq:I0}, the diode quality (or ideality) coefficient is determined by Equation \ref{eq:a}.
\begin{equation}
\label{eq:a}
a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) }
\end{equation}

@@

First is necessary to correct the energy consumption that was estimated to the load ($E_{consumption}$). That is done by Equation \ref{eq:Ecorrected}, according \cite{Pinho}. Where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.
\begin{equation}
\label{eq:Ecorrected}
E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }
\end{equation}

The total minimum number of solar panels necessary($ N_{TPmin} $) is calculated by Equation \ref{eq:NTPmin}, and the check is done with the Equation \ref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from Equation \ref{eq:NTPmin}.
\begin{equation}
\label{eq:NTPmin}
N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}
\end{equation}

@@

Particularly, the total number of panels is series ($ N_{PSmin} $) and parallel ($ N_{PPmin} $) are given by the Equations \ref{eq:NPSmin} and \ref{eq:NPPmin}, respectively. With the check did by Equations \ref{eq:NPS} and \ref{eq:NPP}. $ V_{system} $ is the DC voltage of the bus, and is a design decision (normally 12, 24 or 48 V).
\begin{equation}
\label{eq:NPSmin}
N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}
\end{equation}

@@

Several models have been presented in the literature, as shown by \cite{Copetti}, and \cite{Manwell93}.
%, and \cite{Manwell94}. 
However, regardless of the model, normally the following parameters are required:

\begin{itemize}
\item Nominal capacity ($ q_{max} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery
%, under predetermined discharge conditions.
\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. 
%Obviously $ 0<SOC<1 $. 
If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
%\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). 
%It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
%\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
\end{itemize}
